Through the eyes of the teacher

### 2021-02-02 paper_1/schrott/paper_1_supplement_with_presence.tex
creating word + pdf paper1_supplement

\caption{Example for set-up during a mini-lesson}\label{fig:datacollection}
\end{figure}

@@

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\tightlist
\item
  Classroom management
  \includegraphics{paper_1_supplement_without_presence_files/figure-latex/classroom management line plots-1.pdf}
  \newpage
\item
  Positive climate and motivation
  \includegraphics{paper_1_supplement_without_presence_files/figure-latex/Positive climate and motivation line plots-1.pdf}
  \newpage
\item
  Clarity and structuredness
  \includegraphics{paper_1_supplement_without_presence_files/figure-latex/Clarity and structuredness line plots-1.pdf}
  \newpage
\item
  Activation and support
  \includegraphics{paper_1_supplement_without_presence_files/figure-latex/Activation and support line plots-1.pdf}
\end{enumerate}

@@

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\setcounter{enumi}{7}
\tightlist
\item
  Natural behaviour
  \includegraphics{paper_1_supplement_without_presence_files/figure-latex/Natural behaviour line plots-1.pdf}
  \newpage
  In addition, we plotted all scales. Graph provides boxplots and individual data for experts and novices.
  \includegraphics{paper_1_supplement_without_presence_files/figure-latex/boxplot scales-1.pdf}
  \newpage
  Furthermore, the duration of the speaking time during the lesson was estimated in the questionnaire by external and self-assessment. The following graph shows the duration of speaking time for experts and novices evaluated by the observer, the students and the teacher.
\end{enumerate}

\includegraphics{paper_1_supplement_without_presence_files/figure-latex/Duration speaking time-1.pdf}
\newpage

>>>>

\caption{Example for set up during a mini-lesson}\label{fig:datacollection}
\end{figure}

@@

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\tightlist
\item
  Classroom management
  \includegraphics{paper_1_supplement_with_presence_files/figure-latex/classroom management line plots-1.pdf}
  \newpage
\item
  Positive climate and motivation
  \includegraphics{paper_1_supplement_with_presence_files/figure-latex/Positive climate and motivation line plots-1.pdf}
  \newpage
\item
  Clarity and structuredness
  \includegraphics{paper_1_supplement_with_presence_files/figure-latex/Clarity and structuredness line plots-1.pdf}
  \newpage
\item
  Activation and support
  \includegraphics{paper_1_supplement_with_presence_files/figure-latex/Activation and support line plots-1.pdf}
  \newpage
\end{enumerate}

{\centering \includegraphics{./pictures/presenceposturegaze}

\caption{(5) Presence: posture/gaze}\label{fig:presenceposturegaze}
\end{figure}

@@

{\centering \includegraphics{./pictures/presencevoice}

\caption{(6) Presence: voice}\label{fig:presencevoice}
\end{figure}
\newpage

{\centering \includegraphics{./pictures/presenceverbalnonverbalintervention}

\caption{(7) Presence: verbal and non-verbal intervention}\label{fig:presenceverbalnonverbalintervention}
\end{figure}
\newpage

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\setcounter{enumi}{7}
\tightlist
\item
  Natural behaviour
  \includegraphics{paper_1_supplement_with_presence_files/figure-latex/Natural behaviour line plots-1.pdf}
  \newpage
  In addition, we plotted all scales. Graph provides boxplots and individual data for experts and novices.
  \includegraphics{paper_1_supplement_with_presence_files/figure-latex/boxplot scales-1.pdf}
  \newpage
  Furthermore, the duration of the speaking time during the lesson was estimated in the questionnaire by external and self-assessment. The following graph shows the duration of speaking time for experts and novices evaluated by the observer, the students and the teacher.
\end{enumerate}

\includegraphics{paper_1_supplement_with_presence_files/figure-latex/Duration speaking time-1.pdf}
\newpage

### 2021-02-02 paper_1/schrott/paper_1_supplement_without_presence.tex
creating word + pdf paper1_supplement

\caption{\label{tab:demographicspilottable}Demographic Informationand and Teaching Experience}

@@

The table below provides an overview over the mean, min, max and standard deviation of all scales.

@@

\caption{\label{tab:table all scales}Mean values of all scales}

>>>>

\caption{\label{tab:demographicspilot1table}Demographic Informationand and Teaching Experience}

@@

\ref{tab:allscales} The table provides an overview over the mean, range and standard deviation of all scales.

@@

\caption{\label{tab:allscales}Mean values of all scales}
